Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-01-24 RNARedPrint.tex
Updates from ShareLaTeX

\revised{Eventually our proof-of-concept results 
 on a comprehensive multi-target RNA design benchmark~\citep{Taneda2015} 
  suggest that our sampling strategy well supports designing biologically relevant
RNAs for multiple targets.}

>>>>

\revised{Eventually, our proof-of-concept results 
 on a comprehensive multi-target RNA design benchmark~\citep{Taneda2015} 
  suggest that our sampling strategy well supports designing biologically relevant
RNAs for multiple targets.}
